Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-10 report/report.tex
Include papers by Peponis and Zimring

%TODO: Sumarize these
Shape grammer, developed by \textbf{Stiny, 1975}
Space syntax, developed by \textbf{Hillier, 1997}. Analytical method that relies on the existence of

Wayfinding
\textbf{(Peponis, Zimring and Choi, 1990)}.

>>>>

%TODO: Sumarize these
Shape grammer, developed by \textbf{Stiny, 1975} (p_Par01.pdf)
Space syntax, developed by \textbf{Hillier, 1997}. Analytical method that relies on the existence of (p_Par01.pdf, SITM_Introduction.pdf)

Wayfinding
\textbf{(Peponis, Zimring and Choi, 1990)}. (p_Par01.pdf, Peponis...pdf)
